Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-25 articles/cycle/alps-cycle.tex
Rephrase acknowledgements. Second draft complete!

\authorcontribution{%
    J.~Seguinot designed the study, ran the simulations, and wrote most of
    the manuscript. All authors contributed to the text.}

@@

    This manuscript builds largely upon a previous study on the Cordilleran Ice
    Sheet which is part of J.~Seguinot's PhD thesis. The experimental design
    used here, as well as the general layout of this study, are in important
    proportions the work of Irina Rogozhina, Arjen~P. Stroeven, Martin Margold and
    Johan Kleman without whom this study would not have happened. As always, we
    are very thankful to Constantine Khroulev, Ed Bueler, and Andy Aschwanden
    for providing constant help and development with PISM, in particular with
    recent issues with the computation of ice temperature (Github issue
    no.~371) and with the computation of bedrock deformation (Github issues
    no.~370 and 377). We are equally thankful to Giovanni Monegato and Marc
    Lüether for very insightful discussions of preliminary model results during
    the European Geoscience Union General Assembly~2017.

>>>>

\authorcontribution{%
    J.~Seguinot designed the study, ran the simulations, and wrote most of
    the manuscript. M.~Huss provided modern ice thickness data. All authors
    contributed to the text. The idea for this study stems in part from an
    excursion organised by F.~Preusser in the central Alps in 2012.}

@@

    This manuscript is partly based on a previous study on the Cordilleran Ice
    Sheet which is part of J.~Seguinot's PhD thesis. The experimental design
    used here, as well as the general layout of this study, are in important
    proportions the work of Irina Rogozhina, Arjen~P. Stroeven, Martin Margold and
    Johan Kleman without whom this study would not have happened. As always, we
    are very thankful to Constantine Khroulev, Ed Bueler, and Andy Aschwanden
    for providing constant help and development with PISM, in particular with
    recent issues with the computation of ice temperature (Github issue
    no.~371) and with the computation of bedrock deformation (Github issues
    no.~370 and 377). We are equally thankful to Giovanni Monegato and Marc
    Luetscher for very insightful discussions of preliminary model results during
    the European Geoscience Union General Assembly~2017.
